Diagnosis Visualizations

### 2023-06-07 Diagnosis_Vis.Rmd
Made geom_count with less variables

@@

@@

# df with and without depression
No_depressy <- Mothership_Diag %>%
  filter(Disorder_Type != "Mood")

@@

Mothership_Current_Long %>%
  ggplot(aes(x = Disorder_Type, y = Disorder_Present, color = Disorder_Type)) +
  geom_count(alpha = .5)+
  scale_size_area(max_size = 20) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Trauma_C" = "Co Trauma", 
                            "Substance_C" = "Co Substance Use",
                            "Somatic_C" = "Co Somatic",
                            "Psychotic_C" = "Co Psychotic",
                            "OCD_Co_C" = "Co OCD",
                            "Mood_C" = "Co Mood",
                            "Eating_C" = "Co Eating",
                            "BPD_Co_C" = "Co BPD",
                            "Anxiety_C" = "Co Anxiety")) +
  labs(title = "Number of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis") 
```

@@

q <- ggplot(Mothership_Current_Long, aes(
  x = BL_CUDOS,
  y = Disorder_Type,
  fill = Disorder_Type)) +
  # geom_density_ridges(alpha=0.6,
  #                     rel_min_height = 0.05, 
  #                     scale = 2)+
   stat_density_ridges(quantile_lines = TRUE, alpha = 0.6, quantiles = 2, rel_min_height = 0.05, scale = 1.5) +
   scale_x_continuous(
   breaks = c(0, 20, 40, 60),
   limits = c(0, 64)) +
  #theme_ridges() + 
  labs(
    x = "Baseline Score on CUXOS",
    #y = "DSM-5 Disorder Subtype",
    title = title,
    subtitle = subtitle,
    caption = cap) +
   theme_minimal(
    base_size = 10,
    base_family = "Commissioner"
    ) + 
    theme(legend.position = "none",
          axis.ticks = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(
       linewidth = 0.4), 
    axis.title.y= element_blank(),
    plot.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),    
    panel.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),
    plot.title = element_text(
      family = "Commissioner",
        #this is the font
      margin = margin(b = 5),
      colour = dark_col,
      size = 15
    ),
    plot.subtitle = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      family = "Commissioner",
      hjust = 0,
      margin = margin(b = 5),
      halign = 0,
      size = 8
    ),
     plot.caption = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      margin = margin(t = 10),
      size = 8))
```

>>>>

                    Disorder_treat = as.factor(
                      NA
                      ))))),

@@

                  No_Co = as.factor(
                    ifelse(BPD_Co_C == 0 &
                           OCD_Co_C == 0 &
                           Somatic_C == 0 & 
                           Eating_C == 0 &
                           Psychotic_C == 0 &
                           Trauma_C == 0 & 
                           Substance_C == 0 &
                           Mood_C == 0 &
                           Anxiety_C == 0, 1,0)),
                  Other_Co = as.factor(
                    ifelse(OCD_Co_C == 1 & 
                           Somatic_C == 0 & 
                           Eating_C == 0 &
                           Psychotic_C == 0,1,0)),

@@

Mothership_Diag_treat <- Mothership %>%
  filter(!is.na(Disorder_treat))%>%
  filter(!is.na(TxYear))
# df with and without depression
No_depressy <- Mothership_Diag %>%
  filter(Disorder_Type != "Mood")

@@

Mothership_Current_Long %>%
  ggplot(aes(x = Disorder_Type, y = Disorder_Present, color = Disorder_Type)) +
  geom_count(aes(size = after_stat(prop),group = Disorder_Type),alpha = .5)+
  scale_size_area(max_size = 25) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Trauma_C" = "Co Trauma", 
                            "Substance_C" = "Co Substance Use",
                            "Somatic_C" = "Co Somatic",
                            "Psychotic_C" = "Co Psychotic",
                            "OCD_Co_C" = "Co OCD",
                            "Mood_C" = "Co Mood",
                            "Eating_C" = "Co Eating",
                            "BPD_Co_C" = "Co BPD",
                            "Anxiety_C" = "Co Anxiety")) +
  labs(title = "Number of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis") 
```

Mothership_current_Imp <- Mothership %>%
  pivot_longer(
    cols=c(Anxiety_C, Mood_C, Substance_C, Trauma_C, BPD_Co_C,Other_Co,No_Co),
    names_to = 'Disorder_Present') %>%
  filter(value != 0) %>%
  select(!value)  %>%
  filter(!is.na(Disorder_Present))%>%
  filter(!is.na(Disorder_treat))

tabs<-as.data.frame.matrix(xtabs(~Disorder_treat + Disorder_Present, data = Mothership_current_Imp))

anx<-sum(tabs[1,])
bpd<-sum(tabs[2,])
mood<-sum(tabs[3,])
trauma<-sum(tabs[4,])

tabs[1,] <- (tabs[1,] /anx)*100
tabs[2,] <- (tabs[2,] /bpd)*100
tabs[3,] <- (tabs[3,] /mood)*100
tabs[4,] <- (tabs[4,] /trauma)*100

tabs
```

```{r}
Mothership_current_Imp$Disorder_Present
Mothership_current_Imp %>%
  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .5)+
  scale_size_area(max_size = 30) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Trauma_C" = "Trauma", 
                            "Substance_C" = "Substance Use",
                            "Other_Co" = "Other",
                            "No_Co" = "None",
                            "Mood_C" = "Mood",
                            "BPD_Co_C" = "BPD",
                            "Anxiety_C" = "Anxiety")) +
  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis") 
```

@@

q <- ggplot(Mothership_Current_Long, aes(
  x = BL_CUDOS,
  y = Disorder_Type,
  fill = Disorder_Type)) +
  # geom_density_ridges(alpha=0.6,
  #                     rel_min_height = 0.05, 
  #                     scale = 2)+
   stat_density_ridges(quantile_lines = TRUE, alpha = 0.6, quantiles = 2, rel_min_height = 0.05, scale = 1.5) +
   scale_x_continuous(
   breaks = c(0, 20, 40, 60),
   limits = c(0, 64)) +
  #theme_ridges() + 
  labs(
    x = "Baseline Score on CUDOS",
    #y = "DSM-5 Disorder Subtype",
    title = title,
    subtitle = subtitle,
    caption = cap) +
   theme_minimal(
    base_size = 10,
    base_family = "Commissioner"
    ) + 
    theme(legend.position = "none",
          axis.ticks = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(
       linewidth = 0.4), 
    axis.title.y= element_blank(),
    plot.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),    
    panel.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),
    plot.title = element_text(
      family = "Commissioner",
        #this is the font
      margin = margin(b = 5),
      colour = dark_col,
      size = 15
    ),
    plot.subtitle = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      family = "Commissioner",
      hjust = 0,
      margin = margin(b = 5),
      halign = 0,
      size = 8
    ),
     plot.caption = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      margin = margin(t = 10),
      size = 8))
```
